### 2021-06-15 paper/report.tex
Fix a couple of to-dos.

We include two types of tests. Polymerase chain reaction (PCR) tests
directly\comment[id=J]{It is not clear what "directly" means} reveal whether an
individual is infected or not. PCR tests require some days to be processed and there are
aggregate capacity constraints throughout. In contrast, rapid antigen tests yield
immediate results; after a phase-in period, all tests that are demanded will be
performed. Specificity and sensitivity of these tests is set according to data analyzed
in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test relative
to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows our model for rapid
test demand. Schools may require students to be tested regularly. Rapid tests may be
offered by employers for on-site workers. Individuals may demand tests for private
reasons, which include having plans to meet other people\footnote{A positive test will
make them reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if she
tests positive or develops symptoms. The thresholds are higher for tests in a private
setting than for tests at the workplace until mid April and then compliance because of
private reasons becomes higher than compliance at the workplace.\comment[id=J]{Shouldn't
we mention that this is because of availability / high costs?}

@@

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that simulated
infections by age predict the corresponding time series in the data \citep[See][for the
general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as depicted
in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of the share of
recorded cases and use data on whether the reason for a PCR test were symptoms of
CoViD-19 to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.\comment[id=J]{Free parameters also include:

>>>>

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all
tests that are demanded will be performed. Specificity and sensitivity of these tests is
set according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on
the timing of the test relative to the start of infectiousness.
Figure~\ref{fig:antigen_tests} shows our model for rapid test demand. Schools may
require students to be tested regularly. Rapid tests may be offered by employers for
on-site workers. Individuals may demand tests for private reasons, which include having
plans to meet other people\footnote{A positive test will make them reduce their
contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if
she tests positive or develops symptoms. The thresholds are higher for tests in a
private setting than for tests at the workplace until mid April and then compliance
because of private reasons becomes higher than compliance at the
workplace.\comment[id=J]{Shouldn't we mention that this is because of availability /
high costs?}

@@

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that age-specific
simulated infections predict the corresponding time series in the data \citep[see][for
the general method]{McFadden1989}. However, the two sets of time series are not
comparable directly because not all cases will be recorded. We thus model recorded cases
as depicted in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of
the share of recorded cases and use data on whether CoViD-19 symptoms led to a PCR test
in order to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.\comment[id=J]{Free parameters also include:
